Approximation as Differentiation

### 2025-03-31 notes/sec/some-categories-with-biproducts.tex
Why LatGal has finite biproducts.

\noindent and biadditivity of composition arises component-wise. Moreover $\LatGal$ has binary products, with
the product of Galois connections defined component-wise; it follows that $\LatGal$ has biproducts
(\propref{biproduct:from-product-or-coproduct}).

>>>>

\noindent and biadditivity of composition is component-wise. Moreover $\LatGal$ has finite products, with the
trivial 1-point lattice as terminal object, product lattice $X \times Y$ as binary product, and product of
Galois connections defined component-wise; it follows that $\LatGal$ has finite biproducts
(\propref{biproduct:from-product-or-coproduct}).
